### 2019-08-10 thesis.tex
saving this version for any reason

The theory developed during this graduate research analyses the combined
action of nonlinear kinetic instabilities and collisional processes in
the context of solar physics. To contextualize our work within the solar
plasma research, in this appendix, we present a brief review of the
current state-of-art of solar physics, followed by a discussion on the
plasma phenomena related to our study.

\section{Solar and space physics}
\label{sec:solar-physics}
The domain of solar and space physics is the \emph{heliosphere}, a cavity in
the interstellar medium, created by the constant supersonic flow of solar
plasma that permeates the interplanetary space. This region encloses the solar
system and extends for approximately $140\unit{AU}$\footnote{$1\unit{AU}=150
  \times 10^6\unit{km}$, where AU means \emph{astronomical unit}, which is
  defined as the mean distance between the Sun and the Earth.} in the
surrounding galactic space. Its outer limit is the \emph{heliopause}, an
interface zone where the outgoing pressure of the solar plasma balances the
incoming pressure from the interstellar medium. This comet-shaped plasma bubble
\cite{Dialynas2017}, has an inner boundary, the \emph{termination shock}, which
delimits the sphere of absolute influence of the solar plasma. Beyond the
termination shock, at roughly $100\unit{AU}$ from the Sun, extending out to the
heliopause, is the heliosheath. In this region, the solar wind particles start
being subjected to increasing external pressure, transitioning to a subsonic,
turbulent flow that blends and interacts directly with the matter in the local
interstellar medium \cite{NAP13060}. In \autoref{figD1}, we have a depiction of
the regions and boundaries described above, and the current location of both
Voyager missions, that are already outside the heliosphere, in the interstellar
space.
\begin{figure}[h]
  \begin{center}
    \includegraphics[width=0.9\textwidth]{solar_system_env.png}
    \caption{Main boundaries of the heliosphere and the location of both
      Voyager missions.}
      {\footnotesize Credit:}
      \href{https://voyager.jpl.nasa.gov/news/details.php?article_id=112}
      {\footnotesize NASA/JPL-Caltech}{\footnotesize , accessed at 08/08/2019.}
    \label{figD1}
  \end{center}
\end{figure}

As described above, particles ejected by the Sun determine the overall
dynamics of the interplanetary space until the termination shock boundary.
Beyond this limit, the solar wind still has a significant influence on
the nature of the local interstellar space for a long distance up to the
heliopause. As a well established scientific discipline, solar and space
physics can be summarized as to understand the history, evolution, and
physical processes of the most influential object in the space environment
around our home planet and its interaction with the solar system and the
interstellar medium.

>>>>

The theory developed during this graduate research analyses the combined
action of nonlinear kinetic instabilities and collisional processes in
the context of solar physics. To contextualize our work within the solar
plasma research, in this appendix, we present a brief review of the
current state-of-art of solar and space physics research, followed by a
discussion on the solar plasma phenomena related to our study.

\section{Solar and space physics}
\label{sec:solar-physics}
The domain of solar and space physics is the \emph{heliosphere}, a cavity in
the interstellar medium, created by the constant supersonic flow of solar
plasma that permeates the interplanetary space. This region encloses the
solar system and extends for approximately $140\unit{AU}$\footnote{An AU
  (astronomical unit) is defined as the mean distance between the Sun and
  Earth, $1\unit{AU}\approx 150\times 10^6\unit{km}$.} in the surrounding
galactic space. Its outer limit is the \emph{heliopause}, an interface zone
where the outgoing pressure of the solar plasma balances the incoming pressure
from the interstellar medium. This comet-shaped plasma bubble \cite{Dialynas2017},
has an inner boundary, the \emph{termination shock}, which delimits the sphere
of absolute influence of the solar plasma. Beyond the termination shock, at
roughly $100\unit{AU}$ from the Sun, extending out to the heliopause, is the
heliosheath. In this region, the solar wind particles start being subjected to
increasing external pressure, transitioning to a subsonic, turbulent flow that
blends and interacts directly with the matter in the local interstellar medium
\cite{NAP13060}. In \autoref{figD1}, we have a depiction of the regions and
boundaries described above, and the current location of both Voyager missions,
that are already outside the heliosphere, in the interstellar space.
\begin{figure}[h]
  \begin{center}
    \includegraphics[width=0.9\textwidth]{solar_system_env.png}
    \caption{Main boundaries of the heliosphere and the location of both
      Voyager missions.}
      {\footnotesize Credit:}
      \href{https://voyager.jpl.nasa.gov/news/details.php?article_id=112}
      {\footnotesize NASA/JPL-Caltech}{\footnotesize , accessed at 08/08/2019.}
    \label{figD1}
  \end{center}
\end{figure}

As described above, particles ejected by the Sun determine the overall
dynamics of the interplanetary space until the termination shock boundary.
Beyond this limit, the solar wind still has a significant influence on
the nature of the local interstellar space for a long distance up to the
heliopause. As a well established scientific discipline, solar and space
physics work towards developing a better understanding of this vast and
complex dynamic system called heliosphere; where, within, very close to
its most influential object, lies our home planet - Earth.

\subsection{Main topics of solar and space physics research}
\label{topics}
